### 2015-09-24 TalkDECPD/bilder/tikz/SCircum.tex
...

          % Points
          \fill[opacity=1](V0) node[below left] {\( \sigma^0 \)};
		  \fill[opacity=1, red](V0) node[above left] {\( c(\sigma^0) \)} circle (1.5pt);
		  \fill[opacity=0] (V0)  circle (1.5pt);
          \fill[opacity=1] (V1)  circle (1.5pt);
          \fill[opacity=1](V2)   circle (1.5pt);
          \fill[opacity=0] (C02)  circle (1.5pt);
          \fill[opacity=1] (C01) node[below] {\( \sigma^1 \)};
		  \fill[opacity=1, red] (C01) node[above] {\( c(\sigma^1) \)} circle (1.5pt);
          \fill[opacity=0](C12)  circle (1.5pt);
          \fill[opacity=1](C) node[below] {\( \sigma^2\)};
		  \fill[opacity=1, red](C) node[above] {\( c(\sigma^2)\)} circle (1.5pt);

>>>>

          % Points
          \fill[opacity=1](V0) node[below left] {\( v \)};
		  \fill[opacity=1, red](V0) node[above left] {\( c(v) \)} circle (1.5pt);
		  \fill[opacity=0] (V0)  circle (1.5pt);
          \fill[opacity=1] (V1)  circle (1.5pt);
          \fill[opacity=1](V2)   circle (1.5pt);
          \fill[opacity=0] (C02)  circle (1.5pt);
          \fill[opacity=1] (C01) node[below] {\( e \)};
		  \fill[opacity=1, red] (C01) node[above] {\( c(e) \)} circle (1.5pt);
          \fill[opacity=0](C12)  circle (1.5pt);
          \fill[opacity=1](C) node[below] {\( f\)};
		  \fill[opacity=1, red](C) node[above] {\( c(f)\)} circle (1.5pt);
